\plaintitle

### 2017-12-11 docs/papers/IoT2017/paper.tex
updated the layout
no message
updated copyright
switch to CCS 2012 classification

% Copyright
\CopyrightYear{2017}
%\setcopyright{acmcopyright}
\setcopyright{acmlicensed}
%\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}
% DOI
\doi{} %http://dx.doi.org/10.475/123_4}
% ISBN
\isbn{} %123-4567-24-567/08/06}
%Conference
\conferenceinfo{IoT'17,}{October 22--25, 2017, Linz, Austria}
%Price
\acmPrice{\$15.00}

@@

\numberofauthors{4}
\author{%
 \alignauthor{Aron Laszka\\
   \affaddr{Vanderbilt University}\\
   \affaddr{Nashville, TN}\\
   \email{aron.laszka@vanderbilt.edu}}
 \alignauthor{Abhishek Dubey\\
\affaddr{Vanderbilt University}\\
   \affaddr{Nashville, TN}\\
   \email{abhishek.dubey@vanderbilt.edu}}
 \alignauthor{Michael Walker\\
\affaddr{Vanderbilt University}\\
   \affaddr{Nashville, TN}\\
   \email{michael.a.walker.1@vanderbilt.edu}}
    \alignauthor{Doug Schmidt\\
\affaddr{Vanderbilt University}\\
   \affaddr{Nashville, TN}\\
   \email{d.schmidt@vanderbilt.edu}}
}

@@

% TODO!
\category{K.6.m}{Miscellaneous}{Security}
\category{D.4.7}{Organization and Design}{Distributed systems}

@@

>>>>

% Copyright
\CopyrightYear{2017}
\setcopyright{acmlicensed}
\conferenceinfo{IoT 2017,}{October 22--25, 2017, Linz, Austria}
\isbn{978-1-4503-5318-2/17/10}\acmPrice{\$15.00}
\doi{https://doi.org/10.1145/3131542.3131562}

@@

\numberofauthors{4}
\author{%
 \alignauthor{Aron Laszka\\
   \affaddr{Vanderbilt University}\\
%   \affaddr{Nashville, TN}\\
   \email{aron.laszka@vanderbilt.edu}}
 \alignauthor{Abhishek Dubey\\
\affaddr{Vanderbilt University}\\
%   \affaddr{Nashville, TN}\\
   \email{abhishek.dubey@vanderbilt.edu}}
 \alignauthor{Michael Walker\\
\affaddr{Vanderbilt University}\\
%   \affaddr{Nashville, TN}\\
   \email{michael.a.walker.1@vanderbilt.edu}}
    \alignauthor{Doug Schmidt\\
\affaddr{Vanderbilt University}\\
%   \affaddr{Nashville, TN}\\
   \email{d.schmidt@vanderbilt.edu}}
}

@@

\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10002978.10003022</concept_id>
<concept_desc>Security and privacy~Software and application security</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010520.10010553</concept_id>
<concept_desc>Computer systems organization~Embedded and cyber-physical systems</concept_desc>
<concept_significance>300</concept_significance>
</concept>
<concept>
<concept_id>10010583.10010662.10010668</concept_id>
<concept_desc>Hardware~Energy distribution</concept_desc>
<concept_significance>300</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[300]{Security and privacy~Software and application security}
\ccsdesc[300]{Computer systems organization~Embedded and cyber-physical systems}
\ccsdesc[300]{Hardware~Energy distribution}

\vspace{-0.5em}
\printccsdesc
\vspace{-0.5em}

@@

\section*{Acknowledgment}
This work was funded in part by a grant by Siemens Corporation, CT.
